\subsubsection{Second Derivative Test \& Hessian Matrix}
\noindent
Recall from single-variable calculus that if we have a critical point (derivative is 0), we can find whether the point is a minimum or maximum by using the second derivative test. If the second derivative is $<0$ at the critical point, then the critical point is a maximum, and if the second derivative is $> 0$ at the critical point, then the critical point is a minimum. A similar process works in higher dimensions.\\

\noindent
In higher dimensions:
\begin{itemize}
	\item If $f_{xx}$ and $f_{yy}$ are $> 0$ at a critical point, then the critical point is a minimum.
	\item If $f_{xx}$ and $f_{yy}$ are $< 0$ at a critical point, then the critical point is a maximum.
	\item If $f_{xx}$ and $f_{yy}$ don't agree on sign, then the point is a saddle point.
\end{itemize}

\noindent
Although there are only 3 options for what a critical point on a surface can be, we need a process of identifying them hat works for for higher dimensional objects too.

[INSERT IMAGE]

\begin{definition}
	The Hessian Matrix (for $f(x,y)$):
	\begin{equation*}
		H = \begin{bmatrix}
			f_{xx} & f_{xy} \\
			d_{yx} & f_{yy} 
		\end{bmatrix}
	\end{equation*} 
\end{definition}
\noindent
Note that $\det{H} = f_{xx}f_{yy} - f_{xy}^2$.\\

\noindent
If $(x_0, y_0)$ is a critical point:
\begin{itemize}
	\item $\det{H(x_0,y_0) > 0}$ means $(x_0, y_0)$ is an extrema. 
	\begin{itemize}
		\item If $f_{xx}(x_0, y_0) > 0$, then $(x_0, y_0)$ is a minima.
		\item If $f_{xx}(x_0, y_0) < 0$, then $(x_0, y_0)$ is a maxima.
	\end{itemize}
	\item $\det{H(x_0, y_0)} < 0$ means $(x_0, y_0)$ is a saddle point.
	\item $\det{H(x_0, y_0)} = 0$ means the 2nd derivatives test is inconclusive.
\end{itemize}
