\subsection{Isomorphic Vector Spaces}

In working on examples, you might have noticed that certain vector spaces seem nearly the same.
For example, when working with elements as just members of a vector space, there seems to be no difference between $\R^4$ and $\mathcal{M}_{2 \times 2}$, the vector space of $2 \times 2$ matrices with real entries.
We'll formalize this idea of vector spaces being the same and find that all finite dimensional vector spaces of the same dimension and field are the same.

\begin{definition}
	An isomorphism between two vector spaces is an invertible linear map.
	If such a function exists, then the two vector spaces are said to be isomorphic to each other.
\end{definition}

\begin{theorem}
	Two finite dimensional vector spaces over the same field are isomorphic if and only if they have the same dimension.
\end{theorem}
\begin{proof}
	$\implies$: Let $T: V \to W$ be the isomorphism between finite dimensional vector spaces $V$ and $W$.
	So, $\linnull{T} = \{\vec{0}\}$ and $\range{T} = W$, meaning $\dim{\linnull{T}} = 0$ and $\dim{\range{T}} = \dim{W}$.
	So, by the Fundamental Theorem of Linear Maps, $\dim{V} = \dim{W}$. \\
	
	$\impliedby$: Let $V$ and $W$ be finite dimensional vector spaces with the same dimension.
	Let $\{\vec{v_1}, \dots, \vec{v_n}\}$ be a basis for $V$ and $\{\vec{w_1}, \dots, \vec{w_n}\}$ be a basis for $W$.
	Define $T: V \to W$ by
	\begin{equation*}
		T(c_1\vec{v_1} + \dots + c_2\vec{v_n}) = c_1\vec{w_1} + \dots c_n\vec{w_n}.
	\end{equation*}
	The function $T$ is surjective because the $\vec{w}$'s span $W$, meaning we can adjust the scalars to get any vector in $W$ as the output.
	Further, $T$ is injective because the $\vec{w}$'s are linearly independent, meaning $\null{T} = \{0\}$.
	Since $T$ is injective and surjective, it is an isomorphism, meaning $V$ and $W$ are isomorphic.
\end{proof}

\begin{corollary}
	Let $F$ be a field.
	Then all vector spaces with field $F$ and dimension $n$ are isomorphic to $F^n$.
\end{corollary}

\begin{example}
	Show that $\mathcal{M}_{2 \times 2}$ and $\R^4$ are isomorphic.
\end{example}
\begin{answer}
	Both these vector spaces have dimension 4, so they are isomorphic by previous result.
	One simple isomorphism between them is
	\begin{equation*}
		T\left(\begin{bmatrix}
			w & x \\ y & z
		\end{bmatrix}\right) = \begin{bmatrix}
			w \\ x \\ y \\ z
		\end{bmatrix}.
	\end{equation*}
\end{answer}

\begin{theorem}
	Let $V$ and $W$ be finite dimensional vector spaces.
	Then $\mathcal{L}(V,W)$, the vector space of all linear transformations from $V$ to $W$ is finite dimensional with
	\begin{equation*}
		\dim{\mathcal{L}(V,W)} = \dim{V} \cdot \dim{W}.
	\end{equation*}
\end{theorem}