\subsection{Test 2}

\begin{enumerate}[label=\arabic*.]
	\item 
		Find the general form of a particular solution to the differential equation
		\begin{equation*}
			y'' + 10y' + 25y = f(t)
		\end{equation*}
		for each of the following cases:
		\begin{enumerate}[label=(\alph*)]
			\item 
				$f(t) = \cos{(-5t)} + 7t\sin{(-5t)}$
			\item
				$f(t) = te^{-5t}$
		\end{enumerate}
	\item
		Consider the matrix $A = \begin{bmatrix}
			1  & 0 & 6 \\
			3  & 1 & 3 \\
			-3 & 3 & -8
		\end{bmatrix}$. Compute its characteristic polynomial and find all its eigenvalues. Pick one of the eigenvalues and compute a corresponding eigenvector.
	\item
		Choose one of the two parts.
		\begin{enumerate}[label=(\alph*)]
			\item 
				Compute the general solution for the equation $y'' - 5y' + 6y = 6e^{4t} - 10e^{t}$.
			\item Use the method of variation of parameters to find a particular solution to $y'' + 9y = \csc{(3t)}$.
		\end{enumerate}
	\item
		A 1kg mass is attached to a spring with stiffness 8N/m. The damping constant is 6Ns/m. At time $t=0$, an external force $F(t) = 8\sin{(2t)}$ is applied to the system as the mass is pushed rightward from equilibrium with a velocity of 1m/s.
		\begin{enumerate}[label=(\alph*)]
			\item
				Find the displacement function of the mass.
			\item
				Determine the steady-state solution for the system.
			\item
				Write the steady-state solution in the form $A\cos{(\omega t - \phi)}$ indicating the amplitude, frequency, period, and phase-shift.
		\end{enumerate}
	\item
		Choose one of the following two parts.
		\begin{enumerate}[label=(\alph*)]
			\item 
				Consider the following linear system of differential equations with given initial conditions:
				\begin{equation*}
					\begin{cases}
						x_1' = 2x_1 - 3x_2 \\
						x_2' = x_1 - 2x^2
					\end{cases} \text{, } x_1(0)=2 \text{, } x_2(0)=3
				\end{equation*}
				\begin{enumerate}[label=(\roman*)]
					\item
						Write the system in normal form.
					\item
						Show that the vectors $\begin{bmatrix}
							3e^t \\
							e^t
						\end{bmatrix}$ and $\begin{bmatrix}
							e^{-t} \\
							e^{-t} 
						\end{bmatrix}$ are solutions to the homogeneous system.
					\item
						Write the general solution for the system and then compute the unique solution satisfying the initial conditions.
				\end{enumerate}
			\item
				The matrix $A = \begin{bmatrix}
					-1 & 2 \\
					-1 & 3
				\end{bmatrix}$ has eigenvalues $\lambda = -2 \pm i$. Find the general solution to the system $\vec{x}' = A\vec{x}$.
		\end{enumerate}
	\item
		Consider the system $\vec{x}' = \begin{bmatrix}
			2 & -1 \\
			3 & -2
		\end{bmatrix}\vec{x} + \begin{bmatrix}
			2t \\
			3t + 3
		\end{bmatrix}$. It is known that the corresponding homogeneous sysstem has general solution $\vec{x_h} = C_1e^t\begin{bmatrix}
			1 \\
			1
		\end{bmatrix} + C_2e^{-t}\begin{bmatrix}
			1 \\
			3
		\end{bmatrix}$. Find the general solution for the given heterogeneous system.
\end{enumerate}