\subsection{Test 1}

\begin{enumerate}[label=\arabic*.]
	\item 
		Determine if $y - \ln{y} = x^2 + 1$ is an implicit solution to $\dd{y}{x} = \frac{2xy}{y-1}$. Give reasons for your answer.
	\item 
		Find the function $y(x)$ that satisfies the differential equation
		\begin{equation*}
			\dd{y}{x} + 4y - e^{-x} = 0 \text{ and } y(0) = \frac{4}{3}
		\end{equation*}
	\item
		Find the solution to the initial value problem $\dd{x}{t} = x\frac{(t-3)^2}{x+2} \text{, } x(3) = -1$. You may leave the solution in implicit form.
	\item
		Find the general solution to the differential equation $y''' + y'' - 2y = 0$.
	\item
		A tank contains 90kg of salt and 2000L of water. Pure water enters the tank at a rate of 3L/min. The solutions is mixed and drains from the tank at a rate of 6L/min.
		\begin{enumerate}[label=(\alph*)]
			\item
				What is the amount of salt in the tank initially?
			\item 
				Find the amount of salt in the tank after 2 hours.
		\end{enumerate}
	\item
		A detective arrives at a murder scene at noon that has an ambient temperature of $16^{\circ}$C. He measures the temperature of the body as $34^{\circ}$C. He then returns an hour later and measures the temperature of the body as $32^{\circ}$C.
		Assuming the normal body temperature is $37^{\circ}$C, write a differential equation using Newton's law of cooling that models the situation. Describe, without actually solving the equation, how one would solve the equation to find then the murder took place.
\end{enumerate}