\subsubsection{Complex Roots}
\noindent
Although the previous two theorems already cover complex roots, we can simplify solutions that have complex roots into functions we more easily understand.\\

\begin{theorem}
	If an auxiliary equation has roots $\alpha \pm \beta i$, then $C_1e^{\alpha x}\cos{(\beta x)}$ and  $C_2e^{\alpha x}\sin{(\beta x)}$ are fundamental solutions.
\end{theorem}
\begin{proof}
	The two corresponding fundamental solutions are
	\begin{equation*}
		C_1e^{(\alpha + \beta i)x} \text{, } C_2e^{(\alpha - \beta i)x}.
	\end{equation*}
	so the part of the general solution for these two fundamental solutions are
	\begin{equation*}
		C_1e^{(\alpha + \beta i)x} + C_2e^{(\alpha - \beta i)x}.
	\end{equation*}
	Using Euler's formula, we can also write this as
	\begin{equation*}
		C_1 e^{\alpha x}\left( \cos{(\beta t)} + i\sin{(\beta x)} \right) + C_2e^{\alpha x}\left( \cos{(-\beta x)} + i\sin{(-\beta x)} \right).
	\end{equation*}
	Using the fact that $\sin{(-x)} = -\sin{x}$, $\cos{(-x)} = -\cos{x}$ and separating into real and imaginary parts,
	\begin{equation*}
		 = \left[ C_1e^{\alpha x}\cos{(\beta x)} + C_2e^{\alpha x}\cos{(\beta x)} \right] + i\left[ C_1e^{\alpha x}\sin{(\beta x)} - C_2e^{\alpha x}\sin{(\beta x)} \right].
	\end{equation*}
	Simplifying \footnote{\label{note1}In this step the values of $C_1$ and $C_2$ might have changed, but they are still constants.},
	\begin{equation*}
		= e^{\alpha x}\left(C_1\cos{(\beta x)} + iC_2\sin{(\beta x)}\right).
	\end{equation*}
	At this point, we need to consider if the constants are real or imaginary.
	We would then take the real part as a fundamental solution.\\
	If they are both real, then a fundamental solution is\footnote{See footnote \ref{note1}}
	\begin{equation*}
		C_1e^{\alpha x}\cos{(\beta x)}.
	\end{equation*}
	where $C_1$ is a real constant.
	If they are both imaginary, the a fundamental solution is\footnote{See footnote \ref{note1}}
	\begin{equation*}
		C_2e^{\alpha x}\sin{(\beta x)}.
	\end{equation*}
	where $C_2$ is a real constant.
\end{proof}

\noindent
If complex roots are repeated, we just add the appropriate number of powers of $x$ in front of both the $\sin{(\beta x)}$ and $\cos{(\alpha a)}$ parts.
\pagebreak % It looked weird having the example start and then the footnote immediately after, so now the example starts on the next page

\begin{example}
	Find the general solution to the following differential equation.
	\begin{equation*}
		y^{(4)} + 2y^{\prime\prime} + y = 0
	\end{equation*}
\end{example}
\noindent
First we extract the auxiliary equation and find its roots.
\begin{equation*}
	r^4 + 2r^2 + 1 = 0 \implies r = i (\text{double root}), -i (\text{double root})
\end{equation*}
Since we have complex roots $0 \pm 1i$, we know that the following are fundamental solutions
\begin{equation*}
	C_1e^{0x}\cos{1x} \to C_1\cos{x} \text{ and } C_2e^{0x}\sin{1x} \to C_2\sin{x}.
\end{equation*}
Since both roots are double roots the following are also fundamental solutions:
\begin{equation*}
	C_3x\cos{x} \text{ and } C_4x\sin{x}.
\end{equation*}
So, the general solution is
\begin{equation*}
	y = C_1\cos{x} + C_2\sin{x} + C_3x\cos{x} + C_4x\sin{x}.
\end{equation*}