\section{Constant Coefficients}
\begin{definition}
	The general form of an nth order linear equation is
	\begin{equation*}
		a_n(x)y^{(n)} + a_{n-1}y^{(n-1)} + \ldots + a_1(x)y' + a_0y = b(x).
	\end{equation*}
	If each $a_i(x)$ is a constant, then the equation has constant coefficients.
\end{definition}

\noindent
We already know how to solve linear first order differential equations using an integrating factor, but let's see if we can develop a method that can solve any order linear, homogeneous differential equation with constant coefficients.

\begin{example}
	Let's try to solve the following equation by guessing and checking likely solutions.
	\begin{equation*}
		y'' - 3y' + 2y = 0
	\end{equation*}
\end{example}
\noindent
Exponentials seem like good guesses. Let's try an exponential of the form $y = Ce^{rx}$ first.
\begin{equation*}
	\left(Ce^{rx}\right)'' - 3\left(Ce^{rx}\right)' + 2\left(Ce^{rx}\right) =  0
\end{equation*}
\begin{equation*}
	Cr^2e^{rx} - 3rCe^{rx} + 2Ce^{rx} = Ce^{rx}\left(r^2 - 3r + 2\right) = 0.
\end{equation*}
Since $Ce^{rx} \neq 0$ unless $C = 0$, we only need to solve the quadratic.
Note that the coefficients of the quadratic are the same as the coefficients in the original differential equation.
\begin{equation*}
	r^2 - 3r + 2 = 0 \implies r = 1 \text{, } 2.
\end{equation*}
So, our two fundamental solutions are
\begin{equation*}
	\begin{cases}
		y = C_1e^{x} \\
		y = C_2e^{2x}
	\end{cases}.
\end{equation*}
Since these two fundamental solutions are linearly independent, the general solution is the sum of the fundamental solutions.
\begin{equation*}
	y = C_1e^{x} + C_2e^{2x}
\end{equation*}

% Auxillary Equation
\input{./higherOrder/constCoeffs/auxillaryEquation.tex}